Efficient Handling of String-Number Conversion

### 2019-11-22 draft.tex

\changed{
We say that a mapping $e:\cvar\cup\#\cvar \rightarrow \nat$ is a \emph{word encoding} a word $w$ (or a $\pa$-encoding of $w$) if $e = \parikhof{x}\cup I$
for some $x \in L(A)$ and $I\in\semof\paf$ such that $w = I(x)$.   
%
Conversely, $w$ is a \emph{$\pa$-decoding} of $e$.
%
We use $\encode \pa(w)$ below to denote all $\pa$-encoding of a word $w$,
and $\decode \pa (e)$ to denote all $\pa$-decodings of a word encoding $e$. Namely,  
% to \emph{word encodings} $e:\cvar\cup\#\cvar \rightarrow \nat$ via the PA $\pa$ and the function $\decode \pa$ does it in the reverse direction.
	$$\encode \pa( w ) = \{e \mid  x \in L(\pa) , I(x) =w, I\in\semof \paf, e = I \cup \parikhof{x}\}$$
	$$\decode \pa(e) =\{ w \mid x \in L(\pa) , I(x) =w, I\in\semof \paf, e = I \cup \parikhof{x} \}$$
Informally, a word encoding $e\in \encode \pa( w )$ means $w$ corresponds to a parametric word $x \in L(\pa)$ whose Parikh image and interpretation of character variables are defined by $e$. Since $e$ has only the information of number of occurrences of character variables (Parikh image), the same word encoding may be shared by multiple words, as formalized in the definition of $\decode \pa(e)$. For the case that $\pa$ is a PFA, by Lemma~\ref{lemma:decoding} each word encoding $e\in \encode \pa( w )$ uniquely encodes the word $w$. The following corollary of Lemma~\ref{lemma:decoding} states that words in $\semof{\pa}$ are decodings of the Parikh image of parametric words in $L(A)$ paired with character variables interpretations satisfying $\paf$:
}

>>>>

\changed{
We say that a mapping $e:\cvar\cup\#\cvar \rightarrow \nat$ is a \emph{word encoding} a word $w$ (or a $\pa$-encoding of $w$) if $e = \parikhof{x}\cup I$
for some $x \in L(A)$ and $I\in\semof\paf$ such that $w = I(x)$.   
%
Conversely, $w$ is a \emph{$\pa$-decoding} of $e$.
%
We use $\encode \pa(w)$ below to denote all $\pa$-encoding of a word $w$,
and $\decode \pa (e)$ to denote all $\pa$-decodings of a word encoding $e$. Namely,  
% to \emph{word encodings} $e:\cvar\cup\#\cvar \rightarrow \nat$ via the PA $\pa$ and the function $\decode \pa$ does it in the reverse direction.
	$$\encode \pa( w ) = \{e \mid  x \in L(\pa) , I(x) =w, I\in\semof \paf, e = I \cup \parikhof{x}\}$$
	$$\decode \pa(e) =\{ w \mid x \in L(\pa) , I(x) =w, I\in\semof \paf, e = I \cup \parikhof{x} \}$$
Informally, that a word encoding $e$ belongs to $\encode \pa( w )$ means that $w$ is an interpretation of a parametric word $x \in L(\pa)$ whose Parikh image and interpretation of character variables are defined by $e$. 
Since $e$ only records the numbers of occurrences of character variables (Parikh image), 
the same word encoding may be shared by multiple words, as formalized in the definition of $\decode \pa(e)$.

If $\pa$ is a PFA, then by Lemma~\ref{lemma:decoding}, each word encoding $e\in \encode \pa( w )$ can be decoded uniquely to the word $w$, i.e.
$$
w = \decode \pa (\encode \pa (w))
$$
Consequently, as stated by the following corollary of Lemma~\ref{lemma:decoding}, 
Parikh image of parametric words in $L(A)$ paired with character variable interpretations satisfying $\paf$ encode precisely the words in $\semof{\pa}$.
%words in $\semof{\pa}$ are precisely the decodings of the Parikh image of parametric words in $L(A)$ paired with character variables interpretations satisfying $\paf$:
}
